Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-05-24 doc/PRF2022/PRF_main.tex
minor changes to organization

Unbouned Flow: 
\begin{enumerate}
\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary conditions using $N=24$ points per particle (FIG. 2). Energy profiles in a linear-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).

\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
Add energy profiles to check local/absolute minimum.

\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), convergence tests using $N=16$ and $N=24$ are not yet verified. 
Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.

\item Use particle/checker board alignment to identify the critical shear rate for phase separation.

@@

%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{shear_0.png}
  \includegraphics[width=0.4\textwidth]{shear_1000.png}\\
  \includegraphics[width=0.4\textwidth]{shear_2000.png}
    \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%

@@

The second set of simulation is putting the equilibrium state of the boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear flow. After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP. Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$. %The deformation starts with stripe separations
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
\end{figure}

>>>>

Unbouned Flow: 
\begin{enumerate}
\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).

\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
Add energy profiles to check local/absolute minimum. Superimpose these
    energies on Figure 3, but scale the energies by the number of Janus
    particles so that it is ``energy per particle"

\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.

\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.

@@

%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.21\textwidth]{shear_0.png}
  \includegraphics[width=0.21\textwidth]{shear_1000.png}
  \includegraphics[width=0.21\textwidth]{shear_2000.png} 
  \includegraphics[width=0.21\textwidth]{shear_2000.png} \\
  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%

@@

The second set of simulation is putting the equilibrium state of the boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear flow. After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP. Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$. %The deformation starts with stripe separations
%
%\begin{figure}
%  \begin{center}
%  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
%  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
%  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
%    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
%\end{figure}
